Matching Bullets

### 2015-12-11 imaging-paper.Rnw
some conclusion work

We have presented ...
\hh{XXX Quick summary of the main points of the paper XXX }

@@

By suggesting an automated algorithm that first identifies lands, then identifies peaks and valleys on this land, we reduce subjectivity and with it possible sources of bias. [T]`he concept of counting striations is subjective and based on experience, but it does tend to be consistent within a single examiner'~\cite{miller:1998}.
For a fair assessment of the adequacy of an algorithm we need transparency. Our matching  algorithm is open: the code is readily available in form of the R package x3rplus~\cite{x3prplus}, and the code to produce this paper is available at \hh{XXX, Eric ... we need a website} \eh{XXX can we just put the GitHub link here?} \hh{github is fine!}. Obviously, this is only a first step, but in times of the Netflix prize~\cite{koren:2009, toescher:2009, piotte:2009} and the many Data Science challenges hosted by Kaggle, we should not let the quality of the matching algorithm be the problem that stands in the way.

>>>>

We have presented an algorithm which detects the most prominent but least relevant structure of a bullet from a ballistics identification perspective, removes these features, and produces residuals which allows for the easy identification of markings. We've generalized this algorithm to align the residuals from two bullets to automatically determine whether they are matches. We created a random forest model using many of the features to provide a probabilistic assessment of the quality of a match, along with the most relevant features. Finally, we've provided an easy-to-use open-source backend, and web frontend to many of these features.

@@

By suggesting an automated algorithm that first identifies lands, then identifies peaks and valleys on this land, we reduce subjectivity and with it possible sources of bias. [T]`he concept of counting striations is subjective and based on experience, but it does tend to be consistent within a single examiner'~\cite{miller:1998}.
For a fair assessment of the adequacy of an algorithm we need transparency. Our matching  algorithm is open: the code is readily available in form of the R package x3rplus~\cite{x3prplus}, and the code to produce this paper is available at \url{http://www.github.com/erichare/imaging-paper}. Obviously, this is only a first step, but in times of the Netflix prize~\cite{koren:2009, toescher:2009, piotte:2009} and the many Data Science challenges hosted by Kaggle, we should not let the quality of the matching algorithm be the problem that stands in the way.
